rotation_runs2019

### 2019-10-04 inst/documents/rotation_runs2019.Rmd
multi-experiment workflow now seems to be working

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(rotations)
library(ggplot2)
library(gridExtra)

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=11, comment=NA}

# options
# i) run each scenario for rotation then sequence and calculate difference in the loop
# ii) run each scenario for rotation then sequence and save gens_under_thresh for each in the output file

nscenarios <- 10

# read an experiment file specifying ranges
inex <- read_in_expt("expt_rot_mort_dispersal.csv", nscenarios=nscenarios)

@@

# run all scenarios
for(i in 1:nscenarios)
{
  linputs <- get_one_in(linmulti, scen_num=i)

@@

@@

@@

@@

    # save object containing inputs and results as rda for analysis
    # by default saved to inst/documents folder
    save(df_res_all, file='df_res_all_rot.rda') #paste0(outFolder,'*.rda'))    
  }

>>>>

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(rotations)
library(ggplot2)
library(gridExtra)
library(readxl) # for reading the excel file that allows me to keep formatting to see inputs clearly

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9, fig.height=5.5, comment=NA, results='asis'}

nscenarios <- 100
plotyn <- 1 #allow turning plots on and off from here

# still deciding how best to do this ...
# infile_multi <- 'rotations-experiments-creating-201909.xlsx'
# infile_multi <- system.file("extdata", infile_multi, package = "rotations", mustWork = TRUE)
# inex_all <- read_excel(infile_multi)

# NOTE to add new files currently need to reinstall package because infiles are in extdata
#infile <- "expt-A2-freq-insame-costs-nodisp.csv"
# infile <- "expt-A4-freq-insame-costs-disp.csv"
# # get the id for the expot to include in outfilenames, specifies experiment attributes
# id_expt <- substr(infile,6,7)
# # read an experiment file specifying ranges
# inex <- read_in_expt(infile, nscenarios=nscenarios)

# now specify an experiment from the multi-experiment file
id_expt <- 'A2'
#id_expt <- 'A4'

inex <- read_in_expt(nscenarios = nscenarios, multi=TRUE, id_expt=id_expt)

# text to go at start of document
cat("Experiment :",id_expt," scenario number is pagenum -1 \n\n    ")

cat("Experiment key :\n    ")
cat("A: resistance frequency threshold, insecticides the same\n    ")
cat("B: resistance frequency threshold, different insecticides\n    ")
cat("C: mortality threshold, insecticides the same\n    ")
cat("D: mortality threshold, different insecticides\n    ")

cat("1: no costs, no dispersal\n    ")
cat("2: costs, no dispersal\n    ")
cat("3: no costs, dispersal\n    ")
cat("4: costs, dispersal\n    ")

@@

# run all scenarios
for(i in 1:nscenarios)
{
  #message should output to the R markdown console
  if (i%%200 == 1) message("scenario ",i," of ",nscenarios," ",Sys.time())

  linputs <- get_one_in(linmulti, scen_num=i)

@@

  linputs$plot <- plotyn #allows setting whether to plot from script
  linputs$add_gens_under50 <- TRUE #to add text to plots of gens under threshold

@@

  #to add label between plots in output doc
  #this adds label underneath, not my intention but does the job
  cat("\n\n\\pagebreak\n    ") #needs results='asis' in the chunk options
  #cat("scenario",i,"\n     ") stopped plots from aligning
  #instead just remember that scenario number is pagenum -1

@@

    #code to rerun approx this scenario
    cat(paste0("run_rot(n_insecticides=",linputs$n_insecticides,", ",
                #"mort_or_freq='",linputs$mort_or_freq,"', ", #quotes dont work, freq is now default
                #'mort_or_freq="',linputs$mort_or_freq,'", ',
                "cost=",signif(linputs$cost,2),", ",
                "start_freqs=",signif(linputs$start_freqs,2),", ", 
                "rot_interval=",linputs$rot_interval,", ",
                "eff=",signif(linputs$eff,2),",\n",
                "dom_sel=",signif(linputs$dom_sel,2),", ",
                "dom_cos=",signif(linputs$dom_cos,2),", ",
                "rr=",signif(linputs$rr,2),", ",
                "expo_hi=",signif(linputs$expo_hi,2),", ",
                "coverage=",signif(linputs$coverage,2),",\n",
                "migration=",signif(linputs$migration,2),", ",
                #"max_gen=",linputs$max_gen,", ", 
                "min_rwr_interval=",linputs$min_rwr_interval,            
                ")\n\n") )

@@

    # save object containing inputs and results as rda for analysis
    # by default saved to inst/documents folder
    save(df_res_all, file=paste0(outFolder,format(Sys.time(), "%Y-%m-%d-%H-%M-"),'df_res_all_rot',id_expt,nscenarios,'.rda')) #paste0(outFolder,'*.rda')) 
    # also save the experiment input file
    save(inex, file=paste0(outFolder,format(Sys.time(), "%Y-%m-%d-%H-%M-"),'inex-',id_expt,'.rda'))   
  }

### 2019-10-04 inst/documents/rotations_notes.Rmd
corrected bugs in rotation_runs2019.Rmd to do with saving rot_interval
multi-experiment workflow now seems to be working

@@

~ how to deal with running seq vs rotations
~ should rotation intervals just be set yearly i.e. 10,20,30 etc.

>>>>

# 2/10/19
corrected bugs in rotation_runs2019.Rmd to do with saving rot_interval

# 3/10/19
rotation_runs2019.Rmd - working for 1000 runs
but progress messages not appearing in terminal
If I knit I do get progress messages and also get a document with all plots but not sure how that will work if running for 10k

~ improved plots so seq and rot on same page
~ changed gens_under_thresh to annotation to make text better

~ gens_under_thresh seemed to be counting 11 for a 10gen rotation ? Seems that a 10 gen rotation doesn't switch until generation 11 etc.
~ AND seemed that rot_interval not passing to run_rot ?

BOTH of these were because exit_rot default was true, now changed default to be false

TWO SEEMING PROBLEMS
prob1) sequence insecticide continues to be used after threshold I expect may be a problem with exit_rot=FALSE
prob2) migration in the new runs seems to make active & refugia the same, maybe I've set limits too high ?
I have default migration set to 0.01 and limits currently set to 0.1 to 0.9
df_res2 <- run_rot(rot_interval = 0, mort_or_freq = 'freq', migration=0.5)

Having difficulty replicating prob1

df_res2 <- run_rot(rot_interval = 0, mort_or_freq = 'freq', migration=0.5)

I set min_rwr_interval to 10 to stop rapid switches for sequence.

run_rot(n_insecticides=2, mort_or_freq='freq', cost=0.013, start_freqs=0.077, rot_interval=10, eff=0.98,
 dom_sel=0.55, dom_cos=0.55, rr=0.47, expo_hi=0.69, coverage=0.23, migration=0.86, max_gen=500,
 min_rwr_interval=1)

note there is a problem with the quotes when copying from the pdf

diagnostics not helpful

Aha, think its just to do with exit_rot = FALSE
run_rot(n_insecticides=2, mort_or_freq='freq', rot_interval=10)

# 4/10/19

Fixed rotation insecticide continues to be used after threshold
which was a bug in insecticide_check() introduced when mort thresholds added

NEW SEEMING PROBLEM
run_rot(n_insecticides=2, mort_or_freq='freq', rot_interval=10, exit_rot=FALSE, diagnostics = TRUE, min_gens_switch_back = 0)
Aha I think problem that insecticide itself is not assessed so keeps being used even when abovbe thresh
FIXED

fixed gens_under_thresh count which had changed to be for all insecticides, not just one.

successfully GOT runs2019 to access the xls file for experiments directly

@@

migration limits ???
I need to check on them more ! to make sure I know what they are doing.
> RAF2 <- rot_migrate(RAF1gen, migration=1, coverage=0.1, verbose=TRUE)
  m.intervention f.intervention m.refugia f.refugia
1              1              1         0         0
2              1              1         0         0
3              1              1         0         0
  m.intervention f.intervention m.refugia f.refugia
1            0.1            0.1       0.1       0.1
2            0.1            0.1       0.1       0.1
3            0.1            0.1       0.1       0.1

CHECK ALL INPUT PARAMS

~ create some plot functions to work on the output files (df_res_all) e.g. plot_rotseq_diff()

~ try to get run progress message into console or terminal
~ improve readme.md with details of how to run simulations

~ maybe just do annual rotation interval i.e. 10 ?
